---
title: "Homework 5"
author: "Nathan Catalano and Brett Simmons"
date: "2023-03-01"
output: html_document
---

Group Members: Nathan Catalano and Brett Simmons

Github repository: https://github.com/BrettSimmons/Lab2


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
choco <- read.csv("https://ds202-at-isu.github.io/labs/data/choco.csv")
head(choco)
```
## Question set 1
###1 What is the overall number of chocolate bars rated?
There are 1,852 chocolate bars rated
```{r}
dim(choco)
```



### 2 How does the number of ratings depend on the year? Draw a bar chart of the number of reports.
```{r}
library(ggplot2)
ggplot(choco, aes(x=Review.Date))+geom_bar(aes(weight=Rating))
```
## Question set 2

### How are ratings distributed? Draw a histogram of ratings and describe it. Don’t forget to mention outliers, if there are any.

```{r}
ggplot(choco, aes(x=Rating)) + geom_histogram(binwidth=.25)
```

### Do ratings depend on the cocoa percentage of a chocolate bar?

###How do ratings compare across different company locations? Focus on the three locations with the most ratings:
